ms2

### 2017-05-25 ms2/ms2.Rmd
moving toward years

hrr = read_tsv('../../db/hrr/hrr.tsv') %>%
  filter(year==2011) %>%
  select(zipcode, hrr) %>%
  left_join(zipcodes, by='zipcode') %>%
  left_join(regions, by='state')

target_year = 2013
all_ineq = read_tsv(sprintf('data/state_ineq_all_%i.tsv', target_year)) %>%
  left_join(regions, by='state')
state_ineq = read_tsv(sprintf('data/state_ineq_%i.tsv', target_year))
hrr_ineq = read_tsv(sprintf('data/hrr_ineq_%i.tsv', target_year))
```

@@

```{r fnz_mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=fnz, color=region, label=state_abbreviation)) +
geom_point() +
geom_text(nudge_x=0.04) +
xlab('claims per beneficiary') +
ylab('fraction of beneficiaries w/ >= 1 claim') +
theme_minimal()
```

@@

```{r nzgini_mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=nzgini, color=region, label=state_abbreviation)) +
geom_point() +
geom_text(nudge_x=0.04) +
xlab('claims per beneficiary') +
ylab('Gini coefficient') +
theme_minimal()
```

@@

# Keep only bug/drug combinations that are in at least 75 HRRs
min_n_states = 35
good_combos = semi_join(abg, possible_bug_drug, by=c('bug', 'drug_group')) %>%
  select(bug, drug_group, state) %>%
  distinct %>%
  count(bug, drug_group) %>% rename(n_places=n) %>%
  filter(n_places >= min_n_states)

@@

summarize_abg = function(df, place_name) {
    group_by_(df, 'bug', 'drug_group', place_name) %>%
    summarize(mean_percent_nonsusceptible=weighted.mean(percent_nonsusceptible, sqrt(n_isolates)),
              n_place_antibiograms=n()) %>%
    #filter(!is.na(mean_percent_nonsusceptible)) %>%
    mutate(place_weight=sqrt(n_place_antibiograms))
}

>>>>

hrr = read_tsv('../../db/hrr/hrr.tsv') %>%
  select(zipcode, hrr) %>%
  left_join(zipcodes, by='zipcode') %>%
  left_join(regions, by='state')

years = 2011:2014
read_years = function(template_fn) {
  lapply(years, function(y) read_tsv(sprintf(template_fn, y)) %>% mutate(year=y)) %>%
    bind_rows()
}

all_ineq = read_years('data/state_ineq_all_%i.tsv') %>%
  group_by(state) %>%
  summarize(mean_cpb=mean(mean),
            sem_cpb=sd(mean)/sqrt(n()),
            mean_fnz=mean(fnz),
            sem_fnz=sd(fnz)/sqrt(n()),
            mean_nzgini=mean(nzgini),
            sem_nzgini=sd(nzgini)/sqrt(n())) %>%
  left_join(regions, by='state')

state_ineq = read_years('data/state_ineq_%i.tsv')
hrr_ineq = read_years('data/hrr_ineq_%i.tsv')
```

@@

Error bars show the s.e.m. across the four data years.

```{r fnz_mean}
all_ineq %>%
  mutate_at(vars(matches('fnz')), function(x) x*100) %>%
  ggplot(aes(x=mean_cpb, xmin=mean_cpb-sem_cpb, xmax=mean_cpb+sem_cpb,
             y=mean_fnz, ymin=mean_fnz-sem_fnz, ymax=mean_fnz+sem_fnz,
             color=region, label=state_abbreviation)) +
  geom_point() +
  geom_linerange() +
  geom_errorbarh(height=0) +
  geom_text(nudge_x=0.04) +
  xlab('mean claims per beneficiary') +
  ylab('mean % beneficiaries with at least one claim') +
  theme_minimal()
```

@@

Error bars show the s.e.m. across the four data years.

```{r nzgini_mean}
all_ineq %>%
  ggplot(aes(x=mean_cpb, xmin=mean_cpb-sem_cpb, xmax=mean_cpb+sem_cpb,
             y=mean_nzgini, ymin=mean_nzgini-sem_nzgini, ymax=mean_nzgini+sem_nzgini,
             color=region, label=state_abbreviation)) +
  geom_point() +
  geom_linerange() +
  geom_errorbarh(height=0) +
  geom_text(nudge_x=0.04) +
  xlab('mean claims per beneficiary') +
  ylab('mean Gini coefficient') +
  theme_minimal()
```

@@

# Keep only the abundant bug/drug combinations
min_n_states = 35
good_combos = semi_join(abg, possible_bug_drug, by=c('bug', 'drug_group')) %>%
  select(bug, drug_group, state) %>%
  distinct %>%
  count(bug, drug_group) %>% rename(n_places=n) %>%
  filter(n_places >= min_n_states)

@@

summarize_abg = function(df, place_name) {
    group_by_(df, 'bug', 'drug_group', place_name) %>%
    summarize(mean_percent_nonsusceptible=weighted.mean(percent_nonsusceptible, sqrt(n_isolates)),
              n_place_antibiograms=n()) %>%
    mutate(place_weight=sqrt(n_place_antibiograms))
}
